---
title: "Air France Business Case"
author: "Panchali Chaudhury"
date: "11/7/2021"
output: html_document
---

# Air France Business Case: Optimizing SEM strategy

Air France media contacts team wants to develop a SEM marketing campaign in order to maximize ROA and increase their ticket sales. Because of the short time the have, they want us to analyse the different search engines that Air France worked with in July 2007. They share with us the data provided by "Double-Click" and we start by looking into the frequency histograms, the statistics summary for each variable and the scatterplots between variables in order to identify possible correlations.

```{r setup, echo = FALSE, message = FALSE, warning = TRUE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = TRUE
)
#Downloading the libraries we are going to use
library(readxl)
library(plotrix)
library(plotly)
library(ggplot2)
library(caret)
library(mlbench)
library(rpart)
library(rpart.plot)
library(ROCR)

# Importing the data
my_first_data <- read_excel("Air France Case Spreadsheet Supplement.xls")

# Massaging our data: Eliminating one line because it doesn't make sense that they made sells if they didn't got clicks
my_data <- my_first_data[ -which((my_first_data$Clicks == 0)&(my_first_data$Amount != 0)) , ]

#Printing summary statistics for the main variables
print("Summary Statistics for Clicks")
summary(my_data$Clicks)
print("Summary Statistics for Cost")
summary(my_data$`Click Charges`)
print("Summary Statistics for Impressions")
summary(my_data$Impressions)
print("Summary Statistics for Income")
summary(my_data$Amount)
print("Summary Statistics for Engine Click Thru Ratio")
summary(my_data$`Engine Click Thru %`)
print("Summary Statistics for Transaction Convertion")
summary(my_data$`Trans. Conv. %`)

# Creating an UDF to calculate mean and standard deviation
stats <- function(var1 , var2)
                {
                  result <- data.frame("Mean","Standard Deviation")
                  for (i in 1:var1) 
                    {
                      result[i,1] <- round(mean(unlist(var2[,i])),3)
                      result[i,2] <- round(sd(unlist(var2[,i])),3)
                    }
                  return(result)  
                }
# Using the UDF in order to get the stats for each search engine 
variable_stats_1 <-  stats( 9 , my_data [ , c(12,13,14,16,17,18,19,20,22)] )
rownames(variable_stats_1) <- c("Search Engine Bid", "Clickc", "Cost", "Impressions", "Engine Click Thru %", "Average Possition", "Transaction Covnertion", "Income", "Bookings")
print(variable_stats_1)

#Plotting graphs
ggplot(data=my_data, aes(x=Clicks, y=Amount, color=`Click Charges`))+
      geom_point()
hist(my_data$`Avg. Pos.`, col = "steelblue4", border = "black", main = "Arverage position in searches")
    pie_amount <-aggregate(Amount ~ `Publisher Name`, data = my_data, sum)
    pie3D(pie_amount[,2], labels=round(pie_amount$Amount/sum(pie_amount$Amount),3)*100 ,main = "Total Income", explode = 0.1, col = hcl.colors(length(pie_amount$Amount), "Spectral"), shade = 0.5) 
    legend("topright", pie_amount[,1], fill = hcl.colors(length(pie_amount$Amount), "Spectral"), cex = 0.65 )
    
    pie_cost <-aggregate(`Click Charges` ~ `Publisher Name`, data = my_data, sum)
    pie3D(pie_cost[,2], labels=round(pie_cost$`Click Charges`/sum(pie_cost$`Click Charges`),3)*100 ,main = "Total Cost", explode = 0.1, col = hcl.colors(length(pie_cost$`Click Charges`), "Spectral"), shade = 0.5) 
    legend("topright", pie_cost[,1], fill = hcl.colors(length(pie_cost$`Click Charges`), "Spectral"), cex = 0.65 )
    
    pie_click <-aggregate(Clicks ~ `Publisher Name`, data = my_data, sum)
    pie3D(pie_click[,2], labels=round(pie_click$Click/sum(pie_click$Clicks),3)*100 ,main = "Total Clicks", explode = 0.1, col = hcl.colors(length(pie_click$Clicks), "Spectral"), shade = 0.5) 
    legend("topright", pie_click[,1], fill = hcl.colors(length(pie_click$Clicks), "Spectral"), cex = 0.65 )


```

## Analysing Search Engines

In order to find the engines that delivered the highest value, we develop KPI from that information like Revenue, ROA and Probability for Booking. And we define our business success and business failure by comparing all different values with the mean and assign 1 to every value that was adobe the mean and 0 for those who weren't.


```{r KPI, echo = FALSE, message = FALSE, warning = TRUE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = TRUE
)

# Creating valuable KPI as variables
my_data$Revenue <- my_data$Amount - my_data$`Total Cost`
my_data$ROA <- my_data$Revenue / my_data$`Total Cost`
my_data$Probability_Book <- my_data$`Total Volume of Bookings` / my_data$Impressions

# Creating an UDF to calculate the mean and standard deviation for each variable of interest (KPI)
stats <- function(var1 , var2)
                {
                  result <- data.frame("Mean","Standard Deviation")
                  for (i in 1:var1) 
                    {
                      result[i,1] <- round(mean(unlist(var2[,i])),3)
                      result[i,2] <- round(sd(unlist(var2[,i])),3)
                    }
                  return(result)  
                }

# Using the UDF in order to get the stats for each search engine 
variable_stats <-  stats( ncol(my_data)-23 , my_data [ , 24:ncol(my_data)] )

# Creating new variables to assing binaries to each observation KPI that are adobe the mean 
    my_data$Revenue_bin <- ifelse( my_data$Revenue > variable_stats[1,1],1,0)
    my_data$ROA_bin <- ifelse( my_data$ROA > variable_stats[2,1],1,0)
    my_data$Probbook_bin <- ifelse( my_data$Probability_Book > variable_stats[3,1],1,0)

```

## Business Insights



## A creative solution that will agile the process in future oportunities

Once we got the results, we wanted to compare 2 different logical regression functions (glm and Gini trees) to define the best one for our purpose. Finally we came out with a process that could lead us to test if our designed campaigns were suitable and had a high probability of being successful. This process can optimize also future campaigns and will solve possible future time inconvenience.

```{r pressure, echo = FALSE, message = FALSE, warning = TRUE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = TRUE
)

#Creating training and test data frames
index_engine <- sample(1:nrow(my_data), size=0.8*nrow(my_data))
my_data_train <- my_data[index_engine,]
my_data_test <- my_data[-index_engine,]

# Using GLM function to get logistic regressions for binary variables
glm_engines_r <- glm( Revenue_bin ~ `Search Engine Bid` + Clicks + `Click Charges` + Impressions + `Avg. Pos.` + Amount, data = my_data_train, family = "binomial")
summary(glm_engines_r)
glm_engines_R <- glm( ROA_bin ~ `Search Engine Bid` + Clicks + `Click Charges` + Impressions + `Avg. Pos.` + Amount, data = my_data_train, family = "binomial")
summary(glm_engines_R)
glm_engines_p <- glm( Probbook_bin ~ `Search Engine Bid` + Clicks + `Click Charges` + Impressions + `Avg. Pos.` + Amount, data = my_data_train, family = "binomial")
summary(glm_engines_p)

# Creating Gini trees for binary variables
ginitree_engine_r <- rpart(Revenue_bin ~ `Search Engine Bid` + Clicks + `Click Charges` + Impressions + `Avg. Pos.` + Amount, data = my_data_train, method =  "class", cp = 0.015)
ginitree_engine_R <- rpart(ROA_bin ~ `Search Engine Bid` + Clicks + `Click Charges` + Impressions + `Avg. Pos.` + Amount, data = my_data_train, method =  "class", cp = 0.015)
ginitree_engine_p <- rpart(Probbook_bin ~ `Search Engine Bid` + Clicks + `Click Charges` + Impressions + `Avg. Pos.` + Amount, data = my_data_train, method =  "class", cp = 0.015)

# Confusion matrix for engine glm functions
prediction_engine_r <- predict(glm_engines_r , my_data_test, type = "response")
confusionMatrix(data = as.factor(as.numeric(prediction_engine_r > 0.5)), reference = as.factor(as.numeric(my_data_test$Revenue_bin)))
pred_engine_r <- prediction(prediction_engine_r, my_data_test$Revenue_bin)
perf_engine_r <-  performance(pred_engine_r, "tpr", "fpr")

prediction_engine_R <- predict(glm_engines_R , my_data_test, type = "response")
confusionMatrix(data = as.factor(as.numeric(prediction_engine_R > 0.5)), reference = as.factor(as.numeric(my_data_test$ROA_bin)))
pred_engine_R <- prediction(prediction_engine_R, my_data_test$ROA_bin)
perf_engine_R <-  performance(pred_engine_R, "tpr", "fpr")

prediction_engine_p <- predict(glm_engines_p , my_data_test, type = "response")
confusionMatrix(data = as.factor(as.numeric(prediction_engine_p > 0.5)), reference = as.factor(as.numeric(my_data_test$Probbook_bin)))
pred_engine_p <- prediction(prediction_engine_p, my_data_test$Probbook_bin)
perf_engine_p <-  performance(pred_engine_p, "tpr", "fpr")

# Performance test for engine Gini trees
predictgini_engine_r <- predict(ginitree_engine_r, my_data_test, type = "prob")
predictiongini_engine_r <- prediction(predictgini_engine_r[,2], my_data_test$Revenue_bin)
performance_engine_r <- performance(predictiongini_engine_r, "tpr", "fpr")
plot(performance_engine_r, color = "black")
plot(perf_engine_r, col="turquoise4", add = TRUE)

predictgini_engine_R <- predict(ginitree_engine_R, my_data_test, type = "prob")
predictiongini_engine_R <- prediction(predictgini_engine_R[,2], my_data_test$ROA_bin)
performance_engine_R <- performance(predictiongini_engine_R, "tpr", "fpr")
plot(performance_engine_R, color = "black")
plot(perf_engine_R, col="turquoise4", add = TRUE)

predictgini_engine_p <- predict(ginitree_engine_p, my_data_test, type = "prob")
predictiongini_engine_p <- prediction(predictgini_engine_p[,2], my_data_test$Probbook_bin)
performance_engine_p <- performance(predictiongini_engine_p, "tpr", "fpr")
plot(performance_engine_p, color = "black")
plot(perf_engine_p, col="turquoise4", add = TRUE)

# Plotting Gini trees
rpart.plot(ginitree_engine_R, type=1, extra=1, cex = 0.75, tweak = TRUE, xflip = TRUE, box.palette = c("steelblue4", "turquoise4"))
rpart.plot(ginitree_engine_p, type=1, extra=1, cex = 0.75, tweak = TRUE, xflip = TRUE, box.palette = c("steelblue4", "turquoise4"))
rpart.plot(ginitree_engine_r, type=1, extra=1, cex = 0.75, tweak = TRUE, xflip = TRUE, box.palette = c("steelblue4", "turquoise4"))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
